---
title: "draft_manuscript"
author: "Megan_Duchesne"
date: "2024-09-15"
output: pdf_document
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tinytex)
library(trackdown)
library(rmarkdown)
library(grateful)
library(tidyverse)
library(rticles)
library(trackdown)
library(here)
library(renv)
library(dplyr)
library(openxlsx)
library(tidyr)
library(assertr)

```

# Purpose:

Introduce range shifts and how few studies are capable of testing long term empirical response of native species to novel competition despite its importance. cite some sources. emulating @grant2006 using mandarte data.

## Research question:

Is there evidence of selection on bills in a population of native song sparrows *(Melospiza melodia)* in response to decades of competition with a larger and more dominant population of fox sparrows *(Passerlla u...)*.

The process of collecting morphological and survival data used in my study are described in detail by @conserva2006. Mark re-capture analysis estimate the re-sighting probability to be 0.988 [@wilson2007].





# Data

**Raw**

The raw survival and averaged morphology data are accessible via the following code:

```{r}
# Raw survival data
surv<-read.xlsx("Project/00_Raw_data/survival_LDP.xlsx", na.strings=c(".", "NA"))

# Raw averaged morphological data
morphology<-read.xlsx("Project/00_Raw_data/morphology_LDP.xlsx", na.strings=c(".", "NA"))

```

**Processed**

The processed data following cleaning and merging are accessible via the following code:

```{r}
# cleaned survival data
surv_cleaned<-read.xlsx("Project/02_outdata/survival_1975-2023_updated_23Sep2024_MD.xlsx", na.strings=c(".", "NA"))

# cleaned morphological data
morphology_cleaned<-read.xlsx("Project/02_outdata/morphology_1975-2023_updated_23Sep2024_MD.xlsx", na.strings=c(".", "NA"))

# selection data: merged survival and morphological data
selection<-read.xlsx("selection_1975-2023_updated_24Sep2024_MD.xlsx", na.strings=c(".", "NA"))
```





# Statisical methods:
** Data cleaning**

** Analyses **




# Results:




# Reference List:
